title

### 2024-11-21 index.qmd
working on analysis. rough draft needs trim

---
title: title
shorttitle: A Short title # aog-article-pdf
shortauthors: Isaiah      # aog-article-pdf
authors:
  - name: Isaiah Espinoza
    email: gespinoz@umd.edu
    roles: author
    affiliation:
      - name: University of Maryland
        department: Department of Government and Politics
        city: College Park
        state: MD
        country: US
reference-section-title: References
date: "2024-10-16"
crossref:
  custom: 
    - key: hyp
      kind: float
      reference-prefix: H
      latex-env: hypothesis # required for PDF format

---

@@

## Intro

@@

Although election officials undertake great efforts to enhance the trustworthiness of election administration, public *trust* in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015]. Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019 ;@stewart2022]. Thus, measures taken by election officials can be undermined, trivialized, or made irrelevant depending on how one feels after the election results have come out.

@@

-   when distinguished by partisanship...
-   moreover, broken down by other demographic variables such as race, gender, education, etc.
-   holding these factors constant demonstrates a [increased/decreased] likelihood that a respondent's confidence would likely [increase/decrease], expectations of fraud would likely [increase/decrease], and concerns for safety would lessen among those in the treatment group compared to those in the control. These results allow us to attribute the differences to the treatment stimulus, namely, the prospect of having veterans serve as election staff or volunteers.

@@

Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996]. Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024]. In addition to ensuring election admin offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections. In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@classen2008; @hall2009; @hall2007]. Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007]. These somewhat generic issues of election worker staffing, competence, and voting technology were likely mere stepping stones leading to more intense election administration issues.

@@

Interventions aimed at improving public trust, or rather, aimed at easing election anxieties may not be within the usual repertoire election officials draw upon. Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a]. Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @classen2008]. Such studies focused on the quality of the voter experience with reference to the interaction between voter and election worker.

@@

The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021. After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterants2022; @nflfootballoperations2022]. Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts[^4] [@powerthepolls2020; @herndon2020]. Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020]. Recruitment efforts in 2022 targeted young students, lawyers, and military veterans [@wang2022].

One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a]. Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results[^5] (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024]. This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020]. Although such media output reeks of the contemporary political context, prior research has substantiated such a connection between veterans and militia groups. @cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience. Most of these veterans actively sought out such groups, as opposed to being recruited by them" [-@cooter2024; see also @cooter2013]. Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation. Yet such speculation is just that.

@@

[^4]: Prior to 2021, I found one online recruitment brochure intent on recruiting veterans to serve as election workers [@studentveteransofamerica2020].

@@

To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties, a recent survey experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland (UMD). The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S. citizens 18 years of age or older. Survey participants were randomly assigned to read one of two fabricated news articles (i.e., vignettes) about recruitment efforts for election jobs.

Participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election. The vignettes were identical save for mention of the group targeted for election work recruitment efforts. The treatment vignette focused on the announcement of a program by county election officials designed to recruit military veterans and their family members from the community, whereas the control vignette omitted mention of "military veterans and their family members", leaving in place "members of the community"[^6]. It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignettes due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022]. In addition, the survey includes a series of items which ask specifically about Maricopa County, AZ and a comparable series of questions about one's local area[^7].

[^6]: Complete text of treatment and control vignettes are included in the Appendix

[^7]: The setting of the vignettes and inclusion of duplicate questions in the survey are highlighted and discussed later as a potential limitation.

Over the past two decades it became commonplace for national polls to gauge public confidence in election administration by asking some variety of the question, "How confident are you that your vote [will be/was] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022]. In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration. Such questions inquire into the voter experience with the institution more directly. This study borrows, modifies, or takes inspiration from certain questions found within the 2022 SPAE and other survey items used by the Pew Research Center [@dunn2018]. These survey items comprise the dependent variables[^8].

[^8]: All survey items are included in the Appendix.

The outcomes of interest (i.e., dependent variables) are broadly referred to as *election anxieties*, but more specifically refer to concern over fairness and accuracy of the election administration; expectations of fraudulent activity intent on manipulating the electoral outcomes; and concern for voter safety, i.e., comfort voting in-person as it relates to expectations of violence, threats, or intimidation.

The first outcome of interest regards trust and confidence in the electoral process, which refers to trust and confidence in the integrity and security of the electoral systems, administration, technology, and people or organizations to fairly and accurately conduct elections. Survey items  measured the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats. The first hypothesis is as follows:

::: {#hyp-1}

### Hypothesis 1

Trust and confidence in election administration will be higher among those who were presented information about efforts to recruit veterans as election workers compared to those who were not

Survey participants also responded to questions asking about expectations of fraudulent activity intent on manipulating the electoral outcome.

The second outcome of interest regards an individual's personal safety concerns about the prospect of voting in-person at a polling site. That is, the extent people feel safe enough to cast a vote at polling sites free from violence, threats of violence, or intimidation.

The primary independent variable is the prospect of military veterans as poll workers. It was considered that veterans would elicit high degrees of approval and support for whatever cause or issue presented. For example, I'd expect high approval and support for recruiting veterans to baseball teams just as much as for recruiting them to work as election staff. Asking participants whether they supported programs intent on recruiting veterans to work as election staff would garner support regardless of the target group. Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require survey questions designed to determine whether veterans have any special effect on electoral confidence and voter safety distinct from the generally high admiration observed most often.

The literature concerning public regard for veterans gives substantial reason to expect that publicized efforts to recruit veterans to work as election staff and volunteers would have the effect of easing election anxieties.

This is a one-sided directional hypothesis. Previous research on public perception and regard for U.S. military veterans gives credence to the directional hypothesis [@kleykamp2018; @kleykamp2023].

Simply put, anything special about veterans that influences people's trust and confidence in election administration is expected to be observable in participants' survey responses. However, exactly what makes veterans special in this regard will not; this study did not inquire into details of public perception about veterans specifically (e.g., positive stereotypes, typical characteristics).

The goal was to determine whether there is anything special in having veterans volunteer as election staff (i.e., poll workers). That is, does it make any difference in terms of concerns over election security, fairness, and voter safety to include veterans as election staff and volunteers compared to other groups? The extent people believe veterans are more trustworthy as election workers than non-veterans in general is difficult without comparable groups to consider.

A series of survey questions sought to determine whether support for veterans as election staff would be notably higher when compared to other relatively neutral groups.

It was hypothesized that different versions of statements in a series of survey questions would result in consistent response effects.

@@

# Appendix {.appendix}

::: {.content-visible when-format="html" unless-format="pdf"}

```{r}
#| label: tbl-desc
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

@@

@@

::: {.content-hidden unless-format="pdf"}

```{r}
#| label: tbl-desc-pdf
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

frqs <- data |> 
  select(qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |>
  map(count_prop)

kableExtra::kbl(demog_df,
                booktabs = T, 
                digits = 2,
                col.names = c("Name", "n", "Pct")) |> 
  kableExtra::pack_rows("Qset", 1, 2) |> 
  kableExtra::pack_rows("Age", 3, 10) |> 
  kableExtra::pack_rows("Gender", 11, 13) |> 
  kableExtra::pack_rows("Education", 14, 17) |> 
  kableExtra::pack_rows("Race", 18, 22) |> 
  kableExtra::pack_rows("Party ID", 23, 25) |> 
  kableExtra::kable_styling(
    latex_options = c("striped", "scale_down"),
    full_width = F,
    font_size = 8) |> 
  kableExtra::column_spec(1, width = "20em")

```{r}
#| label: tbl-desc-pdf-2

tbl.desc <- data |> 
  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99"))) |> 
  labelled::set_variable_labels(
    age_cat = "Age group, in years",
    gender_3cat = "Gender",
    race = "Race",
    educ_4cat = "Highest level of education completed",
    milserv1 = "Prior service in the Armed Forces",
    milserv2 = "Currently serving in the Armed Forces",
    milservfam = "Member of immediate family served or is currently serving",
    voted2020 = "Turnout in 2020",
    choice2020 = "Vote Choice 2020",
    voteintent = "Vote Intent 2024",
    ideo = "Political Ideology",
    ideolean = "Political Ideology, lean",
    partyid_3cat = "Party ID"
  ) |>
  gtsummary::tbl_summary(
    by = qset,
    include = c(
      age_cat,
      gender_3cat,
      race,
      educ_4cat,
      partyid_3cat,
      ideo,
      ideolean,
      voted2020,
      choice2020,
      voteintent,
      milserv1,
      milserv2,
      milservfam
    ),
    statistic = list(gtsummary::all_categorical() ~ "{n} ({p}%)"),
    type = list(
      milserv1 ~ "categorical",

      milserv2 ~ "categorical",
      milservfam ~ "categorical"
    ),
    missing = "no"
  ) |>
  gtsummary::add_n() |>
  gtsummary::add_overall() |>
  gtsummary::modify_header(label = "**Variable**") |>
  gtsummary::bold_labels()

gtsummary::as_kable_extra(
  tbl.desc, 
  booktabs = T,
  digits = 2,
  addtl_fmt = T,
  linesep = ""
) |> 
  kableExtra::kable_styling(
    latex_options = c("striped", "scale_down"),
    font_size = 9)

-   limitations: interpretations of the treatment effect are limited.
  -   The sample may not be generalizable to the population.
  -   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts. 
  -   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups. 
  -   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons. 
    -   First, the vignettes and many survey questions ask about Maricopa County, AZ specifically. Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence. Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S. they've know nothing about. Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree.
    -   Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ. Consequently, many questions within the questionnaire were duplicates with that one differences. This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that likely resulted in a higher drop off rate. More importantly, the quality of responses were likely diminished to some unknown extent. Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice. It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated; after completing a long series on Maricopa County, participants then answered the same questions about the local community. The rate to which participants dropped from the survey is ___, which suggests fatigue as an important factor. Survey fatigue is a known issue that should be taken into consideration. Comparison of treatment effects between the MC series and the local area series is undermined by the unknown influence that fatigue would have on response choices. Any differences couldn't confidently be attributed to "my area" vs Maricopa county. We also can't determine whether treatment effects are sustained when comparing the Maricopa County series to the local area series asked subsequently. We would have to assume the setting as irrelevant, which we can't reasonably do.

@@

# Appendix A: Survey Experiment Vignettes {#sec-appendix-a}

::::: {#fig-vignettes layout-ncol=2 .content-visible when-format="html" unless-format="pdf"}
::: {#fig-treatment}
### Treatment Vignette

Text of the Treatment Condition: Recruitment of Veterans and Military Family Members
:::

Text of the Control Condition: Recruitment of Community Members
:::

::::: {#fig-vignettes layout-ncol=2 .content-hidden unless-format="pdf"}
::: {#fig-treatment}
### Treatment Vignette

Text of the Treatment Condition: Recruitment of Veterans and Military Family Members
:::

Text of the Control Condition: Recruitment of Community Members
:::

>>>>

---
title: title
subtitle: subtitle
shorttitle: A Short title # aog-article-pdf
shortauthors: Isaiah      # aog-article-pdf
authors:
  - name: Isaiah Espinoza
    email: gespinoz@umd.edu
    roles: author
    affiliation:
      - name: University of Maryland
        department: Department of Government and Politics
        city: College Park
        state: MD
        country: US
reference-section-title: References
date: "2024-10-16"
date-modified: today
crossref:
  custom: 
    - key: hyp
      kind: float
      reference-prefix: H
      latex-env: hypothesis # required for PDF format
---

@@

## Introduction

@@

Although election officials undertake great efforts to enhance the trustworthiness of election administration, public *trust* in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015]. Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019; @stewart2022]. Thus, measures taken by election officials can be undermined, trivialized, or made irrelevant depending on how one feels after the election results have come out.

@@

-   when distinguished by partisanship...
-   moreover, broken down by other demographic variables such as race, gender, education, etc.
-   holding these factors constant demonstrates a \[increased/decreased\] likelihood that a respondent's confidence would likely \[increase/decrease\], expectations of fraud would likely \[increase/decrease\], and concerns for safety would lessen among those in the treatment group compared to those in the control. These results allow us to attribute the differences to the treatment stimulus, namely, the prospect of having veterans serve as election staff or volunteers.

@@

Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996]. Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024]. In addition to ensuring election admin offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections. In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@claassen2008; @hall2009; @hall2007]. Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007]. These somewhat generic issues of election worker staffing, competence, and voting technology were likely mere stepping stones leading to more intense election administration issues.

@@

Interventions aimed at improving public trust, or rather, aimed at easing election anxieties may not be within the usual repertoire election officials draw upon. Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a]. Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @claassen2008]. Such studies focused on the quality of the voter experience with reference to the interaction between voter and election worker.

@@

The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021. After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022]. Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts[^5] [@powerthepolls2020; @herndon2020]. Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].

One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a]. Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results[^6] (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024]. This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020]. Although such media output reeks of the contemporary political context, prior research has substantiated such a connection between veterans and militia groups. @cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience. Most of these veterans actively sought out such groups, as opposed to being recruited by them" [-@cooter2024; see also @cooter2013]. Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation. Yet such speculation is just that.

@@

@@

To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties, a recent survey experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland (UMD). The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S. citizens 18 years of age or older.

The primary independent variable is the prospect of military veterans as poll workers. It was considered that veterans would elicit high degrees of approval and support for whatever cause or issue presented. For example, I'd expect high approval and support for recruiting veterans to baseball teams just as much as for recruiting them to work as election staff. Asking participants whether they supported programs intent on recruiting veterans to work as election staff would garner support regardless of the target group. Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment and questions designed to determine whether veterans have any special effect on electoral confidence and voter safety distinct from the generally high admiration observed most often.

Survey participants were randomly assigned to read one of two fabricated news articles (i.e., vignettes) about recruitment efforts for election jobs. Participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election. The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran; whereas the control vignette simply omitted any mention of veterans and their family members, and didn't describe "Jordan Braxton" as an Army veteran. Beyond those small differences and the headlines, the article vignettes are identical. Any effects can be attributed to the information about veterans in the treatment vignette[^7].

It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignettes due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022]. In addition, the survey includes a series of items which ask specifically about Maricopa County, AZ and a comparable series of questions about one's local area[^8].

Over the past two decades it became commonplace for national polls to gauge public confidence in election administration by asking some variety of the question, "How confident are you that your vote \[will be/was\] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022]. In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration. Such questions inquire into the voter experience with the institution more directly. This study borrows, modifies, or takes inspiration from certain questions found within the 2022 SPAE and other survey items used by the Pew Research Center [@dunn2018]. These survey items comprise the dependent variables[^9].

The outcomes of interest (i.e., dependent variables) are broadly referred to as *election anxieties*, but more specifically refer to confidence over fairness and accuracy of the election administration; expectations of fraudulent activity intent on manipulating the electoral outcomes; and concern for voter safety, i.e., comfort voting in-person as it relates to expectations of violence, threats, or intimidation. The following presents multiple one-sided directional hypotheses. Previous research on public perception and regard for U.S. military veterans gives credence to the directional hypotheses [@kleykamp2018; @kleykamp2023].

The first outcome of interest regards *trust and confidence* in election administration, which includes the integrity and security of the electoral process, administration, technology, and people or organizations to fairly and accurately conduct elections. Survey items measured the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, as well as confidence that the voting process will be fair.

The first hypothesis is as follows:

$H_{1}:$ Trust and confidence in election administration will be higher among those who were presented information about efforts to recruit veterans as election workers compared to those who were not

In total, six survey items measure different aspects of trust and confidence in election administration. These items were analyzed individually but were also transformed into a composite scale of trust and confidence.

The literature concerning public regard for veterans gives substantial reason to expect that publicized efforts to recruit veterans to work as election staff and volunteers would have the effect of easing election anxieties. As such, survey participants also responded to a series of questions that inquired into expectations of electoral fraud---i.e., fraudulent activity intent on manipulating the electoral outcome.

Note, however, that an *expectation* of electoral fraud implies a degree of distrust more so than an agitated state of anxiety over the *potential* for electoral fraud. Conceptually, this may be considered a particular kind of 'anxiety' given that is it pre-election (hence, an expectation), however, not necessarily. A person may be rather confident with regard to how much they distrust the integrity of electoral administration, resulting in such expectations.

For instance, the first item of the 5-item series asks participants to report their expectation that "There will be voter fraud, that is, people who are not eligible to vote will vote or vote more than once" on a 4-option response scale ranging from "Not likely at all" to "very likely". This statement, as well as the rest in the series, asserts an expected compromise of election integrity, which speaks to the trustworthiness of the institution. What the individual expects, more or less, is that electoral fraud will occur, implying that fraudulent attempts will be successful.

It was expected that the experimental stimulus would result in lower expectation for electoral fraud among those who read the treatment vignette compared to those who read the control vignette. The second hypothesis is,

$H_{2}:$ Expectations of electoral fraud will be lower among those who were presented information about efforts to recruit veterans as election workers compared to those who were not

Another outcome of interest regards concerns about voting in-person at a polling site, i.e., voter safety. That is, the extent people feel that voters are safe enough to cast a vote at polling sites free from violence, threats of violence, or intimidation. Two survey items use slightly different questions to inquire about the same essential issue—i.e., perceptions of physical safety at the polls. The third hypothesis follows,

$H_{3}:$ Concerns for voter safety be lower among those who are presented information about efforts to recruit veterans as election workers compared to those who are not

Another outcome of interest concerned how particular actions of election officials, or circumstances at polling sites, would impact the confidence of election integrity as well as voter safety *from the perspective of survey respondents*. Survey participants responded to a series of six statements, all prefaced with the same question, "Regardless of whether any of these are actually the case, how would the following impact your confidence in the fairness and accuracy of elections conducted this November?" The six statements were,

1.  Election officials test every machine used in the election to ensure they are secure.
2.  Election officials conduct audits of ballots after every election to confirm the results were accurate.
3.  Poll watchers affiliated with the political parties or candidates observe the election.
4.  Election staff and volunteers include military veterans and their family members from the community.
5.  Election staff and volunteers include lawyers from the community.
6.  Election staff and volunteers include college students from the community.

For each statement, survey participants responded by selecting one of five response options:

1.  Decrease confidence a lot
2.  Decrease confidence somewhat
3.  No impact on confidence
4.  Increase confidence somewhat
5.  Increase confidence a lot

It was expected that respondents would estimate stronger impact on their confidence given they were assigned to read the treatment vignette compared to those who were not. Thus, the hypothesis is,

$H_{4}:$ Respondents who read the treatment vignette will report stronger impact on their personal confidence in fairness and accuracy of election administration when veterans are stated to be included among election staff and volunteers compared to those who read the control vignette.

The extent people believe veterans are more trustworthy as election workers than non-veterans in general is difficult without comparable groups to consider. Recruitment efforts in 2022 targeted young students, lawyers, and military veterans [@wang2022]. Thus, lawyers and college students were selected as two groups for which responses could be compared between different statement versions.

The goal was to determine whether there is anything special in having veterans volunteer as election staff (i.e., poll workers) compared to other groups. That is, does it make any difference in terms of concerns over election security, fairness, and voter safety to include veterans as election staff and volunteers compared to other groups? The fourth hypothesis, irrespective of the experimental stimulus, reads,

$H_{5}:$ Respondents who read the treatment vignette will report stronger impact on their personal confidence in fairness and accuracy of election administration when veterans are stated to be included among election staff and volunteers compared to identical statements about lawyers or college students.

## Results

@@

-   limitations: interpretations of the treatment effect are limited.
-   The sample may not be generalizable to the population.
-   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
-   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
-   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons. - First, the vignettes and many survey questions ask about Maricopa County, AZ specifically. Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence. Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S. they've know nothing about. Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree. - Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ. Consequently, many questions within the questionnaire were duplicates with that one differences. This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that likely resulted in a higher drop off rate. More importantly, the quality of responses were likely diminished to some unknown extent. Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice. It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated; after completing a long series on Maricopa County, participants then answered the same questions about the local community. The rate to which participants dropped from the survey is \_\_\_, which suggests fatigue as an important factor. Survey fatigue is a known issue that should be taken into consideration. Comparison of treatment effects between the MC series and the local area series is undermined by the unknown influence that fatigue would have on response choices. Any differences couldn't confidently be attributed to "my area" vs Maricopa county. We also can't determine whether treatment effects are sustained when comparing the Maricopa County series to the local area series asked subsequently. We would have to assume the setting as irrelevant, which we can't reasonably do.

## Appendix A: Survey Experiment Vignettes {#sec-appendix-a}

::::: {#fig-vignettes .content-visible layout-ncol="2" when-format="html" unless-format="pdf"}
::: {#fig-treatment}
### Treatment Vignette

| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
| 
|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff. As the U.S. general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
| 
|   Army veteran Jordan Braxton just joined the elections workforce. Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle. I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
:::

| **Local Residents Recruited for Election Jobs in Maricopa County**
| 
|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff. As the U.S. general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
| 
|   Jordan Braxton just joined the elections workforce. Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle. I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
:::

::::: {.content-hidden layout-ncol="2" unless-format="pdf"}
<div>

### Treatment Vignette

</div>

<div>

### Control Vignette

Text of the Control Condition: Recruitment of Community Members

</div>
:::::

## Appendix B: Sample Demographics {#sec-appendix-b}

::: {.content-visible when-format="html" unless-format="pdf"}
```{r}
#| label: tbl-desc
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

@@

```
:::

::: {.content-hidden unless-format="pdf"}
```{r}
#| label: tbl-desc-pdf
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

frqs <- data |> 
  select(group, qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |> 
  map(count_prop)

kableExtra::kbl(demog_df,
                booktabs = T, 
                digits = 2,
                col.names = c("Name", "n", "Pct")) |> 
  kableExtra::pack_rows("Experiment Condition", 1, 2) |>
  kableExtra::pack_rows("Question Set", 3, 4) |>
  kableExtra::pack_rows("Age", 5, 12) |> 
  kableExtra::pack_rows("Gender", 13, 15) |> 
  kableExtra::pack_rows("Education", 16, 19) |> 
  kableExtra::pack_rows("Race", 20, 24) |> 
  kableExtra::pack_rows("Party ID", 25, 27) |> 
  kableExtra::kable_styling(
    latex_options = c("striped", "scale_down"),
    full_width = F,
    font_size = 8) |> 
  kableExtra::column_spec(1, width = "20em")

@@

@@

[^6]: Prior to 2021, I found one online recruitment brochure intent on recruiting veterans to serve as election workers [@studentveteransofamerica2020].

[^7]: Complete text of treatment and control vignettes are included in the Appendix

[^8]: The setting of the vignettes and inclusion of duplicate questions in the survey are highlighted and discussed later.

[^9]: All survey items are included in the Appendix.
